signalHsmm with k-mer hidden states

### 2015-07-06 signalHSMM_kMer_report.Rmd
redo report
now report is in concordance with the new signalHsmm

Now let us build a new model on **signalHsmm2010**
```{r}
  parametersSet2 <- add_k_mer_state2(kMer1, signalHsmm2010$pipar, signalHsmm2010$tpmpar, signalHsmm2010$od, 
                                     signalHsmm2010$params, pState1, nState1, pTrans1, d=3)
  parametersSet3 <- add_k_mer_state2(kMer2, pipar = parametersSet2$pipar, tpmpar = parametersSet2$tpmpar, 
                                     od = parametersSet2$od, params = parametersSet2$params,
                                     pState2, nState2, pTrans2, d=3)
  parametersSet4 <- add_k_mer_state2(kMer3, pipar = parametersSet3$pipar, tpmpar = parametersSet3$tpmpar, 
                                     od = parametersSet3$od, params = parametersSet3$params, 
                                     pState3, nState3, pTrans3, d=3)
  parametersSet5 <- add_k_mer_state2(kMer4, pipar = parametersSet4$pipar, tpmpar = parametersSet4$tpmpar, 
                                     od = parametersSet4$od, params = parametersSet4$params, 
                                     pState4, nState4, pTrans4, d=3)
  overall_probs_log <- signalHsmm2010$overall_probs_log
  maxSignal <- 45
```

@@

    viterbi_res <- duration_viterbi2(deg_sample-1, signalHsmm2010$pipar, signalHsmm2010$tpmpar, 
                                     signalHsmm2010$od, signalHsmm2010$params)
    viterbi_path <- viterbi_res[["path"]]+1
    c_site <- ifelse(any(viterbi_path == 4), 
                     max(which(viterbi_path == 3)), 
                     length(deg_sample))
    prob.signal <- viterbi_res[["viterbi"]][c_site, viterbi_path[c_site]]
    prob.non <- Reduce(function(x, y) x + overall_probs_log[y], deg_sample[1L:c_site], 0)
    prob.total <- exp(prob.signal - prob.non)

    viterbi_res5 <- duration_viterbi2(deg_sample-1, parametersSet5$pipar, parametersSet5$tpmpar, 
                                      parametersSet5$od, parametersSet5$params)
    viterbi_path5 <- viterbi_res5[["path"]]+1
    c_site5 <- ifelse(any(viterbi_path5 == 4), 
                      min(which(viterbi_path5 == 4))-1, 
                      length(deg_sample))
    c_site5 <- ifelse(any(viterbi_path5 == lastState1), 
                      min(which(viterbi_path5 == lastState1)), 
                      c_site5)
    c_site5 <- ifelse(any(viterbi_path5 == lastState2), 
                      min(which(viterbi_path5 == lastState2)), 
                      c_site5)
    c_site5 <- ifelse(any(viterbi_path5 == lastState3), 
                      min(which(viterbi_path5 == lastState3)), 
                      c_site5)
    c_site5 <- ifelse(any(viterbi_path5 == lastState4), 
                      min(which(viterbi_path5 == lastState4)), 
                      c_site5)
    #get probabilities of signal peptide model
    prob.signal5 <- viterbi_res5[["viterbi"]][c_site5, viterbi_path5[c_site5]]
    #get probabilities of no signal peptide model
    prob.non5 <- Reduce(function(x, y) x + overall_probs_log[y], deg_sample[1L:c_site5], 0)
    prob.total5 <- exp(prob.signal5 - prob.non5)

@@

  parametersSet2 <- add_k_mer_state2(kMer1, signalHsmm2010$pipar, signalHsmm2010$tpmpar, signalHsmm2010$od, 
                                     params, pState1, nState1, pTrans1, d=3)
  parametersSet3 <- add_k_mer_state2(kMer2, pipar = parametersSet2$pipar, tpmpar = parametersSet2$tpmpar, 
                                     od = parametersSet2$od, params = parametersSet2$params,
                                     pState2, nState2, pTrans2, d=3)
  parametersSet4 <- add_k_mer_state2(kMer3, pipar = parametersSet3$pipar, tpmpar = parametersSet3$tpmpar, 
                                     od = parametersSet3$od, params = parametersSet3$params, 
                                     pState3, nState3, pTrans3, d=3)
  parametersSet5 <- add_k_mer_state2(kMer4, pipar = parametersSet4$pipar, tpmpar = parametersSet4$tpmpar, 
                                     od = parametersSet4$od, params = parametersSet4$params, 
                                     pState4, nState4, pTrans4, d=3)
  overall_probs_log <- signalHsmm2010$overall_probs_log
  maxSignal <- 45
```

@@

>>>>

Now let us build a new model on **signalHsmm2010**
```{r}
  parametersSet2 <- add_k_mer_state(kMer1, signalHsmm2010$pipar, signalHsmm2010$tpmpar, signalHsmm2010$od, 
                                     signalHsmm2010$params, pState1, nState1, pTrans1, d=3)
  parametersSet3 <- add_k_mer_state(kMer2, pipar = parametersSet2$pipar, tpmpar = parametersSet2$tpmpar, 
                                     od = parametersSet2$od, params = parametersSet2$params,
                                     pState2, nState2, pTrans2, d=3)
  parametersSet4 <- add_k_mer_state(kMer3, pipar = parametersSet3$pipar, tpmpar = parametersSet3$tpmpar, 
                                     od = parametersSet3$od, params = parametersSet3$params, 
                                     pState3, nState3, pTrans3, d=3)
  parametersSet5 <- add_k_mer_state(kMer4, pipar = parametersSet4$pipar, tpmpar = parametersSet4$tpmpar, 
                                     od = parametersSet4$od, params = parametersSet4$params, 
                                     pState4, nState4, pTrans4, d=3)
  overall_probs_log <- signalHsmm2010$overall_probs_log
  maxSignal <- 45
```

@@

    viterbi_res <- duration_viterbi(deg_sample-1, signalHsmm2010$pipar, signalHsmm2010$tpmpar, 
                                     signalHsmm2010$od, signalHsmm2010$params)
    viterbi_path <- viterbi_res[["path"]]+1
    c_site <- ifelse(any(viterbi_path == 4), 
                     max(which(viterbi_path == 3)), 
                     length(deg_sample))
    prob.signal <- viterbi_res[["viterbi"]][c_site, viterbi_path[c_site]]
    prob.non <- Reduce(function(x, y) x + overall_probs_log[y], deg_sample[1L:c_site], 0)
    prob.total <- exp(prob.signal - prob.non)

    viterbi_res5 <- duration_viterbi(deg_sample-1, parametersSet5$pipar, parametersSet5$tpmpar, 
                                      parametersSet5$od, parametersSet5$params)
    viterbi_path5 <- viterbi_res5[["path"]]+1
    c_site5 <- ifelse(any(viterbi_path5 == 4), 
                      min(which(viterbi_path5 == 4))-1, 
                      length(deg_sample))
    c_site5 <- ifelse(any(viterbi_path5 == lastState1), 
                      min(which(viterbi_path5 == lastState1)), 
                      c_site5)
    c_site5 <- ifelse(any(viterbi_path5 == lastState2), 
                      min(which(viterbi_path5 == lastState2)), 
                      c_site5)
    c_site5 <- ifelse(any(viterbi_path5 == lastState3), 
                      min(which(viterbi_path5 == lastState3)), 
                      c_site5)
    c_site5 <- ifelse(any(viterbi_path5 == lastState4), 
                      min(which(viterbi_path5 == lastState4)), 
                      c_site5)
    #get probabilities of signal peptide model
    prob.signal5 <- viterbi_res5[["viterbi"]][c_site5, viterbi_path5[c_site5]]
    #get probabilities of no signal peptide model
    prob.non5 <- Reduce(function(x, y) x + overall_probs_log[y], deg_sample[1L:c_site5], 0)
    prob.total5 <- exp(prob.signal5 - prob.non5)

@@

  parametersSet2 <- add_k_mer_state(kMer1, signalHsmm2010$pipar, signalHsmm2010$tpmpar, signalHsmm2010$od, 
                                     params, pState1, nState1, pTrans1, d=3)
  parametersSet3 <- add_k_mer_state(kMer2, pipar = parametersSet2$pipar, tpmpar = parametersSet2$tpmpar, 
                                     od = parametersSet2$od, params = parametersSet2$params,
                                     pState2, nState2, pTrans2, d=3)
  parametersSet4 <- add_k_mer_state(kMer3, pipar = parametersSet3$pipar, tpmpar = parametersSet3$tpmpar, 
                                     od = parametersSet3$od, params = parametersSet3$params, 
                                     pState3, nState3, pTrans3, d=3)
  parametersSet5 <- add_k_mer_state(kMer4, pipar = parametersSet4$pipar, tpmpar = parametersSet4$tpmpar, 
                                     od = parametersSet4$od, params = parametersSet4$params, 
                                     pState4, nState4, pTrans4, d=3)
  overall_probs_log <- signalHsmm2010$overall_probs_log
  maxSignal <- 45
```

@@

save(benchmark_data2, file = "clean_data.RData")
